### 2019-01-23 journal/example.tex
ok

Further, let us only consider two kinds of mutants:  condition-negation and statement deletion mutants.  Obviously, negating the condition on line 3 will make all of our failing test cases pass, and negating the condition on line 7 will make test cases 2 and 3 pass, but not test case 1.  Negating the conditions on lines 4-5, 8-9, and 11-12 will repair our test cases, but is also likely to make some passing test case fail, so these mutants will not be used in our analysis.  Finally, the only statements that can be deleted without breaking the code are deletions of the {\tt corrupt} calls on lines 6, 10, and 13.  We can identify these mutants, which will form the basis of our distance metric and our fault localization, by the line number of the change, since there is only one mutant per line in the set.  Each test can then be associated with a vector of 5 elements:  {\tt (repaired by line 3, repaired by line 6, repaired by line 7, repaired by line 10, repaired by line 13)}.

>>>>

Further, let us only consider two kinds of mutants:  condition-negation and statement deletion mutants.  Obviously, negating the condition on line 3 will make all of our failing test cases pass, and negating the condition on line 7 will make test cases 2 and 3 pass, but not test case 1.  Negating the conditions on lines 4-5, 8-9, and 11-12 will repair our test cases, but is also likely to make some passing test case fail, so these mutants will not be used in our analysis.  Finally, the only statements that can be deleted without breaking the code are deletions of the {\tt corrupt} calls on lines 6, 10, and 13.  We can identify these mutants, which will form the basis of our distance metric and our fault localization, by the line number of the change, since there is only one mutant per line in the set.  Each test can then be associated with a bit-vector of 5 elements:  {\tt (repaired by line 3, repaired by line 6, repaired by line 7, repaired by line 10, repaired by line 13)}.  The vectors for our tests, then, are:

\begin{code}
Test 1: 1 1 0 0 0
Test 2: 1 0 1 1 0
Test 3: 1 0 1 0 1
\end{code}

Test 1 thus has a distance of 0.75 from Test 2 and Test 3.  Test 2 has a distance of only 0.5 from Test 3.  If the Furthest-Point-First algorithm starts from Test 1 it will arbitrarily select either Test 2 or 3 next, then the other test.  If it starts with Test 2 or 3, it will select Test 1 next, then the other of the two closer tests.  Of course, taming a set of three failing tests is not difficult.  However, if we imagine a much larger set of failing tests, which contain irrelevant features that cannot be removed by delta-debugging without causing the programs to become syntactically invalid, so long as the basic structure of the cause for failure remains the same, then the FPF algorithm will select tests by the distance between vectors and still essentially produce Test 2, then 1, then 3, for example.
